ZCB Pricing

### 2018-07-24 ZCB Pricing .Rmd
Modifications to Monte Carlo

bond_price <- function(alpha,beta,sigma,t,T,r){
  A <- (1-exp(-beta*(T-t)))/(beta)
  B <- (1/beta)*((alpha-(sigma)^2/(2*beta))*(A - T +t) - (sigma^(2)*A^2)/(4))
  exp(-A*r +B)
}

@@

monte_carlo <- function(alpha, beta, sigma, t, T, r, n, s){
  # s = number of sub-intervals
  # n = number of simulation trials

@@

```{r}
#Generate normal RV
z=rnorm(1000)
z.=-z

# Another Version of the MOnte Carlo simulations
Crude_Monte_Carlo=function(alpha,beta,sigma,T,r0,n,s){

@@

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*rnorm(1)# Euler Discretization
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  int=exp(-Sum)
  mean=mean(int)
  sd=sd(int)/sqrt(n)
  result=c(mean,sd)
  result
}
```

@@

Antithetic_variates= function(alpha,beta,sigma,T,r0,n,s){
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path_inv= matrix(0,nrow = s+1, ncol = n)# matrix to generate interest paths using inverse RV
  sim_path[1,]= r0
  sim_path_inv[1,]=r0

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i] # Euler Discretization
      dr_i= alpha*(beta-sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i]
      sim_path[j,i]=sim_path[j-1,i]+dr
      sim_path_inv[j,i]=sim_path_inv[j-1,i]+dr_i

@@

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  Sum.=colSums(sim_path_inv[2:(s+1),]*dt)
  int.=exp(-Sum.)
  int=exp(-Sum)# Estimate using the conjugate rates
  Average=(int+int.)/2 # Average of estimates
  mean=mean(Average)
  sd=sd(Average)/sqrt(n)
  result=c(mean,sd)
  result

@@

Moment_Matching=function(alpha,beta,sigma,T,r0,n,s){

@@

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r0
  z=rnorm(s)
  z_m= z-mean(z) # MOMENT MATCHING TRANSFORMATION

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=alpha*(beta-sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i]# Euler Discretization
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  int=exp(-Sum)
  mean=mean(int)
  sd=sd(int)/sqrt(n)
  result=c(mean,sd)
  result
}
```

@@

@@

explicit <- function(alpha,beta,sigma,r,I,T){

@@

X = explicit(0.08,0.8,0.005,0.03,1:50,T=1)
Z <- bond_price(0.08,0.8,0.005,0,1,0.03)

@@

implicit <- function(alpha,beta,sigma,r,I,J,T){
  # I = partition of time interval
  # J = partition of short rate variable

@@

R <- implicit(0.08,0.8,0.005,0.05,1:100,seq(-0.3,0.5,0.01),T=5)

xvec <- seq(-0.3,0.5,0.01)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
  }
plot(R, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Implicit Method vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)
```

@@

>>>>

bond_price <- function(alpha=0.08,beta=0.8,sigma=0.005,t=0,T=1,r=0.08){
  A <- (1-exp(-beta*(T-t)))/(beta)
  B <- (1/beta)*((alpha-(sigma)^2/(2*beta))*(A - T +t) - (sigma^(2)*A^2)/(4))
  exp(-A*r +B)
}

@@

monte_carlo <- function(alpha =0.08, beta=0.8, sigma=0.005, t=0, T=1, r=0.08, n=1000, s=100){
  # s = number of sub-intervals
  # n = number of simulation trials

@@

```{r}

# Another Version of the MOnte Carlo simulations
Crude_Monte_Carlo=function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=1000,s=100){

@@

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*rnorm(1)# Euler Discretization
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  int=exp(-Sum)
  mean=mean(int)
  sd=sd(int)/sqrt(n)
  result=mean
  result
}

@@

Antithetic_variates= function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=1000,s=100){
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path_inv= matrix(0,nrow = s+1, ncol = n)# matrix to generate interest paths using inverse RV
  sim_path[1,]= r0
  sim_path_inv[1,]=r0
  z = rnorm(n)
  z. = -z

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z[i] # Euler Discretization
      dr_i= (alpha-beta*sim_path_inv[j-1,i])*dt + sigma*sqrt(dt)*z.[i]
      sim_path[j,i]=sim_path[j-1,i]+dr
      sim_path_inv[j,i]=sim_path_inv[j-1,i]+dr_i

@@

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  Sum.=colSums(sim_path_inv[2:(s+1),]*dt)
  int.=exp(-Sum.)
  int=exp(-Sum)# Estimate using the conjugate rates
  Average=(int+int.)/2 # Average of estimates
  mean=mean(Average)
  sd=sd(Average)/sqrt(n)
  result= mean
  result

@@

Moment_Matching=function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=1000,s=100){

@@

  #Simulate interest rates
  dt <- T/s # Length of sub-intervals
  sim_path= matrix(0,s+1,n) # Matrix that stores rate pathways
  sim_path[1,]= r0
  z=rnorm(n)
  z_m= z-mean(z) # MOMENT MATCHING TRANSFORMATION

  for (i in 1:n){
    for (j in 2:(s+1)){
      dr=(alpha-beta*sim_path[j-1,i])*dt+sigma*sqrt(dt)*z_m[i]# Euler Discretization
      sim_path[j,i]=sim_path[j-1,i]+dr
    }
  }

  # Monte Carlo Simulations
  Sum=colSums(sim_path[2:(s+1),]*dt)
  int=exp(-Sum)
  mean=mean(int)
  sd=sd(int)/sqrt(n)
  result=mean
  result
}

@@

```{r}

xvec <- seq(-0.3,0.5,0.01)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
}

CR <- NULL
AV <- NULL
MM <- NULL

for (k in 1: length(xvec)){
  CR[k] <- Crude_Monte_Carlo(r0 = xvec[k], T=5)
}

for (s in 1: length(xvec)){
  AV[s] <- Antithetic_variates(r0 = xvec[s], T =5)

for (j in 1: length(xvec)){
  MM[j] <- Moment_Matching(r0 = xvec[j], T =5)

plot(CR, x = xvec[1:length(xvec)],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Monte Carlo vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)
lines(xvec,AV, col ="black", lty =1.5)
lines(xvec,MM, col ="yellow", lty =1.5)
```

@@

explicit <- function(alpha= 0.08,beta=0.8,sigma=0.005,r=0.08,I=1:100,T=2){

@@

#============================================================================================
#Doing some plots
# 
# xvec <- seq(-0.3,0.5,0.01)
# H <- NULL
# for (r in 1:length(xvec)){
#   S[r] <- bond_price(0.08,0.8,0.005,0,1,xvec[r])
# }
# 
# for (i in 1:length(xvec)){
#   H[i] <- explicit(r = xvec[i], I= 1:50, T=5)
# }
# 
# plot(H, x = xvec,xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Crank - Nicolson vs Known Solution")
# lines(xvec,S, col ="blue", lty =1.5)

@@

implicit <- function(alpha= 0.08,beta=0.8,sigma=0.005,r=0.08,I=1:100, J =seq(0,0.10,0.01),T=1){
  # I = partition of time interval
  # J = partition of short rate variable

@@

#============================================================================================

# Doing some plots

xvec <- seq(-0.3,0.6,0.01)
R <- implicit(T=5,J= xvec, I = 1:1250)
S <- NULL
for (r in 1:length(xvec)){
  S[r] <- bond_price(0.08,0.8,0.005,0,5,xvec[r])
  }
plot(R, x = xvec[1:length(xvec)-1],xlab = " Annual Interest Rate",ylab = "Bond Price",type = "l", col ="red", main = "Implicit Method vs Known Solution")
lines(xvec,S, col ="blue", lty =1.5)

@@

```{r}
# Crank Nicolson 2.0

CN_2 <- function(alpha = 0.08,beta =0.8,sigma=0.005,T=5,r =0.05,I = 1:1250, J = seq(-0.3,0.5,0.01)){

  M <- length(J)
